Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-03-13 awipev-CO2.Rmd

```
## Temperatures
Several temperature sensors are on site, 1 inside the Ferrybox and 2 outside:

@@

# # #@@@@@ test plot #@@@@@ #@@@@@ #@@@@@
seafet_contros_xts <- dplyr::select(d_all, datetime, at, ct)#voltINT, phINT_filtered,pH_s_seafet_temp_field, T_seaF, temp_fb, temp_insitu, sal)
#seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
  #dySeries("voltINT", label = "voltINTINT", color ="blue", strokeWidth=0, pointSize=2) %>%
   # dySeries("pH_s_seafet_temp_field", label = "pH spectro", axis= "y2", color =  "green", strokeWidth = 0, pointSize = 4 ) %>%
    #dySeries("pHint_tot_sf", label = "corr pH INT", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
  dySeries("ct", label = "ct", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
dySeries("at", label = "at", color ="blue",axis= "y2", strokeWidth=0, pointSize=2) %>%
  #dySeries("temp_insitu", label = "temp_insitu", color ="black",axis= "y2", strokeWidth=0, pointSize=2) %>%
   # dySeries("T_seaF", label = "T_seaF", color ="grey",axis= "y2", strokeWidth=0, pointSize=2) %>%
 #   dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
  #dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>%
  #dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
   # dyEvent(as.POSIXct("2019-09-02 12:00:00", tz="GMT"), "seaFET #0007 out of water for cleaning", labelLoc = "bottom", color="red") %>%
  dyLegend(show = "auto")   %>%
  #dyAxis( "y2",valueRange = c(-3, 36))%>%
  #dyAxis( "y",valueRange = c(-2, 2))%>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
  dyRangeSelector(height = 30, dateWindow= NULL)
# #@@@@@ #@@@@@ #@@@@@ #@@@@@ #@@@@@

@@

### **FerryBox**
- **2018-11-14**: One instrument was removed by Uwe (Chlorophyl-a), that means that one column (CHl_A_Cyclops) was also removed from the Ferrybox data file. Script was modified in consequence.

>>>>

## Salinities
Several salinity sensors are on site, 1 inside the Ferrybox and 1 outside. Note that several CTD have been replace in situ. The sal_insitu variable combine all these CTD salinity measurements:

- 1 SBE45 inside the Ferrybox (sal_fb)
- 1 CTD at 11 meters depth (sal_insitu)

### **Sal FB / Sal *in situ* **
```{r Sal comparaison, echo=FALSE, message= FALSE, warning=FALSE}

d_all <- d_all%>%
  dplyr::mutate( sal = ifelse(sal <28, NA, sal) ,
                 sal_fb = ifelse(sal_fb <28, NA, sal_fb),
                 sal_insitu = ifelse(sal_insitu <28, NA, sal_insitu))

fit <- lmodel2(data = d_all,  sal_fb ~ sal_insitu , nperm = 99)

p_sal_fb_sal_insitu<-  ggplot(d_all,aes(x=sal_insitu, y= sal_fb, label = month))+
  geom_text( aes(color=factor(month))) + 
 # scale_color_viridis_d(option = "C", guide="none")+
  geom_line(aes(x = sal_fb, y = sal_fb), linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  labs(title = paste("Sal in situ vs Sal FB","\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 )+ scale_colour_discrete(guide="none") +
  labs( x="Salinity insitu", y="Salinity FB ", color = "Months")  +theme_bw()
print(p_sal_fb_sal_insitu)

d_all$diff_sal_fb_insitu <- d_all$sal_insitu - d_all$sal_fb
mean_diff_sal_fb_insitu <- round(mean(d_all$diff_sal_fb_insitu, na.rm = TRUE), digits = 2)
sd_diff_sal_fb_insitu <- round(sd(d_all$diff_sal_fb_insitu, na.rm = TRUE), digits = 2)

The mean difference between salinity FB and in situ is: `r mean_diff_sal_fb_insitu` ± `r sd_diff_sal_fb_insitu`°C.

## Temperatures
Several temperature sensors are on site, 1 inside the Ferrybox and 2 outside:

@@

# # #@@@@@ test plot #@@@@@ #@@@@@ #@@@@@
seafet_contros_xts <- dplyr::select(d_all, datetime, sal_fb, sal_insitu, sal)#voltINT, phINT_filtered,pH_s_seafet_temp_field, T_seaF, temp_fb, temp_insitu, sal)
#seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
  #dySeries("voltINT", label = "voltINTINT", color ="blue", strokeWidth=0, pointSize=2) %>%
   # dySeries("pH_s_seafet_temp_field", label = "pH spectro", axis= "y2", color =  "green", strokeWidth = 0, pointSize = 4 ) %>%
    #dySeries("pHint_tot_sf", label = "corr pH INT", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
  dySeries("sal_insitu", label = "sal_insitu", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
dySeries("sal_fb", label = "sal_fb", color ="blue",axis= "y2", strokeWidth=0, pointSize=2) %>%
  dySeries("sal", label = "sal", color ="black",axis= "y2", strokeWidth=0, pointSize=2) %>%
   # dySeries("T_seaF", label = "T_seaF", color ="grey",axis= "y2", strokeWidth=0, pointSize=2) %>%
 #   dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
  #dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>%
  #dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
   # dyEvent(as.POSIXct("2019-09-02 12:00:00", tz="GMT"), "seaFET #0007 out of water for cleaning", labelLoc = "bottom", color="red") %>%
  dyLegend(show = "auto")   %>%
  #dyAxis( "y2",valueRange = c(-3, 36))%>%
  #dyAxis( "y",valueRange = c(-2, 2))%>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
  dyRangeSelector(height = 30, dateWindow= NULL)
# #@@@@@ #@@@@@ #@@@@@ #@@@@@ #@@@@@

@@

### **FerryBox**

- **2020-03-13**: Salinity was filtered above 28 in d_all.rds file.
- **2018-11-14**: One instrument was removed by Uwe (Chlorophyl-a), that means that one column (CHl_A_Cyclops) was also removed from the Ferrybox data file. Script was modified in consequence.
